### 2024-01-12 documentation/thesis/thesis_document.tex
more thesis

@@

@@

\hypertarget{opensource-projects}{%
\section{Opensource Projects}\label{opensource-projects}}

@@

accomplished

@@

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly. This also fulfills the goal of
making individual user-created algorithms interchangeable. If the user
now wishes to use a different \gls{cad} algorithm instead of the
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
the other steps can simply be preserved.

The individual modules and their functions are explained in detail in
the following chapters.

>>>>

As the following, the motivation for the development of this framework
is listed. A brief introduction to the topic of low-field \gls{mri} is
given, followed by the research problem to be solved by this work.

@@

In this work, reference is made exclusively to the hardware shim
process. Since this project is to be used in the future to construct a
low-field \gls{mri} B0 field magnet from permanent magnets.

@@

@@

@@

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly. This also fulfills the goal of
making individual user-created algorithms interchangeable. If the user
now wishes to use a different \gls{cad} algorithm instead of the
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
the other steps can simply be preserved and only the new step needs to
be implemented.
